---
title: "Appendix for Computaional Social Science Summative"
author: "Z0195806"
date: "`r Sys.Date()`"
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Appendix 1 Dataset Pre-processing

**Dataset World Values Survey Wave 7 (2017-2022)**

Link: <https://www.worldvaluessurvey.org/WVSDocumentationWV7.jsp>

**Dataset V-Dem (2022)**

Link: <https://www.v-dem.net/data/dataset-archive/>

It contains data files and original questionnaire.

I download the dataset from this link and put it in "./data" directory.

## 1.1 Read the data from the RData and RDS file

```{r}
current_directory = getwd()
# print(current_directory)
# actual path = current_directory
setwd(current_directory)
# load("./data/WVS_Cross-National_Wave_7_rData_v5_0.rdata")
# WVS.origin = `WVS_Cross-National_Wave_7_v5_0`
# v_dem_2022 = readRDS("./data/2022_CPD_V_Party_R_v2/V-Dem-CPD-Party-V2.rds")
```

```{r}
# Using dim() to get both rows and columns
# Prints c(number_of_rows, number_of_columns)
# print(dim(WVS.origin))
```

## 1.2 Missing Values Handling

```{r}
# Check if it exists missing value
# any_missing_values = any(is.na(WVS.origin))
# Will print TRUE if there are any NAs, otherwise FALSE
# print(any_missing_values)
```

```{r}
# Remove the rows with missing value
# WVS.origin = na.omit(WVS.origin)
```

```{r}
# head(data.origin)
```

## 1.3 Sample the Dataset

The dataset is still too big to analyse after deleting all the missing values, so I decide to randomly sample $\frac{1}{4}$ of it.

```{r}
# Use ceiling to round up to the nearest integer
# sample_size <- ceiling(0.25 * nrow(data.origin))
# data.sample <-
#   data.origin[sample(1:nrow(data.origin),
#                     size = sample_size,
#                     replace = FALSE), ]
# write.csv(data.sample, "./data/data.csv", row.names = FALSE)
```

# Appendix 2 Read Democracy Dataset Directly

```{r}
dem_data = read.csv("./data/country_level_dem.csv")
```

```{r}
head(dem_data)
```

```{r}
# Using dim() to get both rows and columns
# Prints c(number_of_rows, number_of_columns)
print(dim(dem_data))
```
